Cross Validation Approaches for Penalized Cox Regression

### 2019-05-21 cross-validation.tex
Edits to 1, 2, and 3.1

\newcommand{\ith}{i^\textrm{th}}
\newcommand{\CVE}{\textrm{CVE}}
\newcommand{\MSE}{\textrm{MSE}}
\newcommand{\logit}{\mbox{logit}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\ones}{\mathbbm{1}}
\newcommand{\indic}[1]{\boldsymbol{1}_{\{ #1 \}}}
\newcommand{\mvec}{\mbox{vec}}
\newcommand{\cov}{\mbox{Cov}}
\newcommand{\eqdist}{\overset{{\cal D}}{=}}
\newcommand{\const}{\mbox{const}}
\newcommand{\iid}{\overset{iid}{\sim}}
\newcommand{\diag}{\mbox{{\bf diag}}}
\newcommand{\Diag}{\mbox{Diag}}

@@

\section*{Abstract}
Cross validation is commonly used for selecting tuning parameters in penalized regression, but its use in penalized Cox regression models has received relatively little attention in the literature. Due to its partial likelihood construction, carrying out cross validation for Cox models is not straightforward, and there are several potential approaches for implementation. Here, we propose two new cross-validation methods for Cox regression and compare them to approaches that have been proposed elsewhere. %\note{IS THIS STILL TRUE?  WE SHOULD EDIT THIS SENTENCE: Our simulation studies show that in general, all cross-validation approaches tend to be conservative (i.e., select smaller models than the optimal choice of tuning parameters) for penalized Cox regression models.} 
Our proposed approach of cross-validating the linear predictors seems to offer an attractive balance of performance and numerical stability. We illustrate these advantages using simulated data as well as real data from two genome-wide studies of survival in cancer patients.
\input{main}

>>>>

\newcommand{\ith}{i^\textrm{th}}
\newcommand{\CVE}{\textrm{CVE}}
\newcommand{\MSE}{\textrm{MSE}}
\newcommand{\logit}{\mbox{logit}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\ones}{\mathbbm{1}}
\newcommand{\indic}[1]{\boldsymbol{1}_{\{ #1 \}}}
\newcommand{\mvec}{\mbox{vec}}
\newcommand{\cov}{\mbox{Cov}}
\newcommand{\eqdist}{\overset{{\cal D}}{=}}
\newcommand{\const}{\mbox{const}}
\newcommand{\iid}{\overset{iid}{\sim}}
\newcommand{\diag}{\mbox{{\bf diag}}}
\newcommand{\Diag}{\mbox{Diag}}
\providecommand{\Tr}{^{\scriptscriptstyle\top}}

@@

\section*{Abstract}
Cross validation is commonly used for selecting tuning parameters in penalized regression, but its use in penalized Cox regression models has received relatively little attention in the literature. Due to its partial likelihood construction, carrying out cross validation for Cox models is not straightforward, and there are several potential approaches for implementation. Here, we propose two new cross-validation methods for Cox regression and compare them to approaches that have been proposed elsewhere.
Our proposed approach of cross-validating the linear predictors seems to offer an attractive balance of performance and numerical stability. We illustrate these advantages using simulated data as well as using them to analyze data from a high-dimensional study of survival in lung cancer patients.
\input{main}
